%
%
% Name and header
{\bf\large 7. Biographical Sketches} \addcontentsline{toc}{section}{Biographical Sketches} \\

{\bf\large \noindent{Gregory A. Feiden}} \\
\hrule\vspace{\baselineskip}

% Education Section
\noindent{\bf Education}:
\begin{flushright}
    \begin{tabular*}{\linewidth}{l l @{\extracolsep{\fill}} r}
        2008 -- 2013  &  Ph.D. (Physics \& Astronomy)  &  Dartmouth College  \\
        2004 -- 2008  &  B.S. (Physics)  &  State University of New York at Oswego  
    \end{tabular*}
\end{flushright}
\vspace{0.4\baselineskip}

% Research Experience
\noindent{\bf Appointments}:
\begin{flushright}
	\begin{tabular*}{\linewidth}{l l @{\extracolsep{\fill}} r}
		2016 --        &  Assistant Professor of Astronomy & University of North Georgia \\
		2015 -- 2016   &  Research Scientist    &  Uppsala University \\
        2013 -- 2015   &  Postdoctoral Fellow   &  Uppsala University \\
        2012 -- 2013   &  Gordon F. Hull Graduate Fellow  &  Dartmouth College \\
		2011 -- 2012   &  Neukom Graduate Fellow & Dartmouth College \\
    \end{tabular*}
\end{flushright}
\vspace{0.4\baselineskip}

\noindent{\bf Awards}:
\begin{flushright}
	\begin{tabular*}{\linewidth}{l @{\extracolsep{\fill}} l r}
%	2014         & Uppsala University Rector's travel grant     & 19\,800 SEK \\
%    2014         & Swedish National Space Board travel grant  & 11\,000 SEK \\
    2013 -- 2015 & Uppsala U.\ Postdoctoral Fellowship, Physics \& Astronomy & 840\,000 SEK \\%
	2012 -- 2013 & Gordon F. Hull Graduate Fellowship  & 26\,000 USD \\    
    2011 -- 2012 & Neukom Institute for Computational Science Fellowship & 26\,000 USD
    \end{tabular*}
\end{flushright}
\vspace{0.4\baselineskip}

%\noindent{\bf Research Interests}: 
%\begin{flushright}
%    \parbox{0.99\linewidth}{
%	\noindent Physics of (sub)stellar interiors and atmospheres; Computational stellar evolution; Stellar ages; Convection; Magneto-convection; Stellar populations; Radiative transfer.}
%\end{flushright}
%\vspace{0.4\baselineskip}

\noindent{\bf Experience \& Expertise}:  %\hspace{\fill} {\small (see page 4)}
\begin{center}
	List everything here.
\end{center}
\vspace{0.4\baselineskip}

\noindent{\bf Relevant Publications}: % \hspace{\fill} {\small (see page 4)}
\begin{enumerate}
	\setlength{\itemsep}{0em}
	\item {\bf Feiden, G.~A.} {\it Magnetic Inhibition of Convection and the Fundamental Properties of Low-Mass Stars. III. A Consistent 10 Myr Age for the Upper Scorpius OB Association}, 2016, A\&A, in press.
	
	\item Mann, A.~W., Newton, E.~R., Rizzuto, A.~C., {Irwin}, J., 
	{\bf {Feiden}, G.~A.}, {Gaidos}, E., {Mace}, G.~N., {Kraus}, A.~L., 
	{James}, D.~J., {Ansdell}, M., {Charbonneau}, D., {Covey}, K.~R., 
	{Ireland}, M.~J., {Jaffe}, D.~T., {Johnson}, M.~C., 
	{Kidder}, B., \& {Vanderburg}, A. \emph{Zodiacal Exoplanets in Time (ZEIT) III: A Neptune-sized planet orbiting a pre-main-sequence star in the Upper Scorpius OB Association}, 2016, ApJ, in press. 
	
	\item Stassun, K.~G., {\bf Feiden, G.~A.}, \& Torres, G. {\it Empirical Tests of Pre--Main--Sequence Stellar Evolution Models with Young Eclipsing Binary Stars}, 2014, New Ast.\ Rev., 60, 1.
	
	\item Torres, G., Lacy, C.~H.~S., Pavlovski, K., {\bf Feiden, G.~A.}, {Sabby}, J.~A., {Bruntt}, H., \& {Viggo Clausen}, J. {\it The G+M Eclipsing Binary V530 Orionis: A Stringent Test of Magnetic Stellar Evolution Models for Low--Mass Stars}, 2014, ApJ, 797, 31.
	
	\item Malo, L., Doyon, R., {\bf Feiden, G.~A.}, {Albert}, L., 
	{Lafreni{\`e}re}, D., {Artigau}, {\'E}., {Gagn{\'e}}, J., \& 
	{Riedel}, A. {\it BANYAN. IV. Fundamental Parameters of Low-Mass Star Candidates in Nearby Young Stellar Kinematic Groups---Isochronal Age Determination Using Magnetic Evolutionary Models}, 2014, ApJ, 792, 37.
	
	\item  {\bf Feiden, G.~A.} \& Chaboyer, B. {\it Magnetic Inhibition of Convection and the Fundamental Properties of Low-Mass Stars. II. Fully Convective Main Sequence Stars}, 2014, ApJ, 787, 53.
	
	\item  {\bf Feiden, G.~A.} \& Chaboyer, B. {\it Magnetic Inhibition of Convection and the Fundamental Properties of Low-Mass Stars. I. Stars with a Radiative Core}, 2013, ApJ, 779, 183.
	
	\item {\bf Feiden, G.~A.} \& Dotter, A. {\it The Interior Structure Constants as an Age Diagnostic for Low-Mass, Pre-Main-Sequence Detached Eclipsing Binary Stars}, 2013, ApJ, 765, 86.
	
	\item {\bf Feiden, G.~A.} \& Chaboyer, B. {\it Self-Consistent Magnetic Stellar Evolution Models of the Detached, Solar-Type Eclipsing Binary EF Aquarii}, 2012, ApJ, 761, 30.
	
	\item \textbf{Feiden, G.~A.} \& Chaboyer, B. \emph{Reevaluating the Mass-Radius Relation for Low-Mass, Main Sequence Stars}, 2012, ApJ, 757, 42. 

\end{enumerate}
\vspace{\baselineskip}

\noindent{\bf Advisors and Advisees}:
\begin{flushright}
    \parbox{0.99\linewidth}{
	\noindent {\bf Graduate and Postgraduate Advisors:} Brian Chaboyer (Dartmouth), Nikolai Piskunov (Uppsala), Susanne H\"{o}fner (Uppsala) \\
	\noindent {\bf Graduate Advisees:} Steven Christophe (Paris-Sud / Uppsala) \\
	\noindent {\bf Undergraduate Advisees:} Jaquille Jones (Dartmouth), Jonas Engman (Uppsala) 
	}
	
\end{flushright}
