%

\phantomsection
{\bf\large 10. Budget Narrative} \addcontentsline{toc}{section}{10. Budget Narrative}

Period 1 (02/2017 - 01/2018) and Period 2 (02/2018 - 01/2019). Undergraduates will be housed on campus in the dorms available for summer term students and they will be provided with a full meal plan.

{\bf 10.1 Summary of Personnel \& Work Effort}

\begin{itemize}
	\item[] {\bf PI: Dr. Gregory A. Feiden (Univ. of North Georgia):} We request 3 months of summer salary and benefits per year in 2017 and 2018.  \\
	
	\item[] {\bf Undergraduate Researcher 1 (Univ. of North Georgia):} We request 3 months of stipend, housing, and subsistence support for an undergraduate researcher during summer 2017. This student will be recruited from University of North Georgia's Physics Department.  \\
	
	\item[] {\bf Undergraduate Researcher 2 (Univ. of North Georgia):} We request 3 months of stipend, housing, and subsistence support for an undergraduate researcher during summer 2017. This student will preferably be recruited from University of North Georgia's Mathematics Department. \\
	
	\item[] {\bf Undergraduate Researcher 3 (Univ. of North Georgia):} We request 3 months of stipend, housing, and subsistence support for an undergraduate researcher during summer 2018. This student will be recruited from University of North Georgia's Physics Department. \\
	
	\item[] {\bf Undergraduate Researcher 4 (Univ. of North Georgia):} We request 3 months of stipend, housing, and subsistence support for an undergraduate researcher during summer 2018. This student will preferably be recruited from University of North Georgia's Computer Science Department at the Mike Cottrell College of Business. \\
		
	\item[] {\bf Dr. Bengt Edvardsson (Uppsala Univ.):} No funding requested. \\
	
	\item[] {\bf Dr. Lent C. Johnson (UC San Diego):} No funding requested. \\
	
	\item[] {\bf Dr. Adam L. Kraus (UT Austin):} No funding requested. \\
	
	\item[] {\bf Dr. Andrew W. Mann (UT Austin):} No funding requested. \\
	
	\item[] {\bf Dr. Nikolai Piskunov (Uppsala Univ.):} No funding requested. \\
	
	\item[] {\bf Dr. Aaron C. Rizzuto (UT Austin):} No funding requested. \\
\end{itemize} 

{\bf 10.2 Facilities \& Equipment}

\$1\,500 to purchase a networked RAID5 unit to store and potentially provide access to the model grid data archive. We will also purchase a single 4 TB external hard disk for continual backups of program data. We also request \$300 for software subscription fees for 2 years: Dropbox (file sharing), Paperpile (Reference management), and 

{\bf 10.3 Travel}

We request \$8\,300 for conference travel in Period 1 and \$7\,950 for conference travel during Period 2. The funds will support travel for PI Feiden and two undergraduates each year to present results from this program. The budget includes the cost of covering conference registration fees, transportation, lodging, meals, and other incidentals. During Period 1, we anticipate that PI Feiden will attend the IAU Symposium on Stellar Ages in Elba, Italy and the Winter 2018 AAS meeting in National Harbor, MD. We anticipate that both undergraduates will also attend the Winter 2018 AAS meeting. During Period 2, it is anticipated that the two undergraduates will attend the Winter 2019 AAS meeting along with PI Feiden. In addition to the Winter 2019 AAS, PI Feiden anticipates attending the Cool Stars 20 meeting in Boston, MA. Finally, we anticipate all three researchers will attend the Georgia Regional Astronomy Meeting (GRAM) during Fall 2017 and Fall 2018. Attending GRAM will consist of carpooling and staying a single night at a local hotel. A cost breakdown for each conference is tabulated below. \\

{\bf PI Feiden:}

\begin{center}
\begin{tabular*}{\linewidth}{l c c c c c c}
	Meeting            &  Reg Fee & Transportation & Hotel (per night) & Nights & Meals & Total \\
	\noalign{\smallskip}\hline\hline\noalign{\smallskip}
	IAUS: Stellar Ages & \$500  & \$1200  & \$125 & 5 & \$375 & \$2700 \\
	GRAM 2017          & \$0    & \$50    & \$100 & 1 & \$75  & \$225  \\
	Winter 2018 AAS    & \$500  & \$350   & \$150 & 5 & \$375 & \$1975 \\
	Cool Stars 20      & \$500  & \$300   & \$175 & 5 & \$375 & \$2050 \\
	GRAM 2018          & \$0    & \$50    & \$100 & 1 & \$75  & \$225  \\
	Winter 2019 AAS    & \$500  & \$450   & \$150 & 5 & \$375 & \$2075 \\
\end{tabular*}
\end{center}

{\bf Undergraduate (per student, 2 students to each meeting):}

\begin{center}
\begin{tabular*}{\linewidth}{l c c c c c c}
	Meeting            &  Reg Fee & Transportation & Hotel (per night) & Nights & Meals & Total \\
	\noalign{\smallskip}\hline\hline\noalign{\smallskip}
	GRAM 2017          & \$0    & \$0     & \$100 & 1 & \$75  & \$175  \\
	Winter 2018 AAS    & \$200  & \$350   & \$150 & 5 & \$375 & \$1475 \\
	GRAM 2018          & \$0    & \$0     & \$100 & 1 & \$75  & \$175  \\
	Winter 2019 AAS    & \$200  & \$450   & \$150 & 5 & \$375 & \$1575 \\
\end{tabular*}
\end{center}


{\bf 10.4 Publications}

We request \$2\,000 for publication charges for 2017 and \$2\,500 for 2018. In period 1, we anticipate publishing the first of two papers presenting the model grid. The paper will focus on presenting the model physics, details about the model grid, discussions about the impact of magnetic fields on stellar interior structure, and the influence of magnetic inhibition of convection on stellar fundamental properties. During period 2, we anticipate publishing two papers: (1) the second model grid paper that will present models with photometric conversions and comparisons against cluster CMDs and (2) a paper introducing the full software package we will develop throughout our two year program.